The effects of uncertain context inference on motor adaptation

### 2022-04-12 adaptation/article/article.tex
New figures ready. Started rewriting paper

@@

\subsubsection{Motor adaptation}
It is widely accepted that in order to adapt motor commands to a novel environment, we create and update internal forward models of the outcomes of control signals \citep{Wolpert_Multiple_1998}. We used this principle and chose to make use of an exact Bayesian learner. To adapt to altered dynamics (e.g. a mechanical arm exerting a force on a participant's hand), our model updates the parameters $\phi$ (see Methods) of a context-specific forward model. These updates are done according to \eref{eqn:motor-adaptation}, using the difference between predictions made with the current parameters of the forward model, and the current observation. With this, a posterior estimate on $\phi$, $q(\phi)$ in \fref{fig:model}, is calculated after each trial.

>>>>

Humans have been shown to adapt their movements when sudden or gradual changes to the dynamics of the environment are introduced, a phenomenon called motor adaptation. If the change is reverted, the adaptation is also quickly reverted. Human are also able to adapt to multiple changes in dynamics presented separately, and to be able to switch between adapted movements on the fly. Such switching relies on contextual information which is often noisy or misleading, which affects the switch between adaptations. Recently, the COIN computational model for motor adaptation and context inference was introduced, which contains explicit components of context inference and Bayesian motor adaptation. This model was used to show the effects of context inference on learning rates across different experiments. We expanded on that work by using the COIN model to show that the effects of context inference on motor adaptation and control go further than previously shown. Here, we used the COIN model to simulate classical motor adaptation experiments from previous works and showed that context inference, and how it is affected by the presence and reliability of feedback, effect a host of behavioral phenomena that had so far required multiple hypothesized mechanisms, lacking a unified explanation. Concretely, we show that the reliability of direct contextual information, as well as noisy sensory feedback, typical of many experiments, effect measurable changes in switching-task behavior, as well as in action selection, that stem directly from imprecise context inference.

@@

\subsubsection{Motor adaptation}
It is widely accepted that in order to adapt motor commands to a novel environment, we create and update internal forward models of the outcomes of control signals \citep{Wolpert_Multiple_1998}. We used this principle and chose to make use of an exact Bayesian learner. To adapt to altered dynamics (e.g. a mechanical arm exerting a force on a participant's hand), our model updates the parameters $\phi$ (see Methods) of a context-specific forward model. These updates are done according to \eref{eqn:update-full}, using the difference between predictions made with the current parameters of the forward model, and the current observation. With this, a posterior estimate on $\phi$, $q(\phi)$ in \fref{fig:model}, is calculated after each trial.
